### 2021-08-17 sections/appendix/descrete_event_simulation/main.tex
Edit minor things
Apply minor changes from review
Apply changes based on Alex's suggestions

The constructed model simulates a queueing system with two waiting spaces and 
two types of individuals. 
The expected behaviour of the nodes in Ciw have been modified such that 
individuals moving from waiting zone 2 into waiting zone 1 may remain blocked 
if there are more than \(T\) individuals in waiting zone 1.

The same performance measures described in sections 
\ref{sec:waiting_time}, \ref{sec:blocking_time} and 
\ref{sec:proportion_within_target} can also be calculated using the DES model.
The simulation can be ran a number of times to eliminate stochasticity and the
outcomes of the two methods can be directly comparable.

% TODO: Include the queueing model diagram here?
% TODO: Include python code here?

>>>>

The constructed model simulates a queueing system with two waiting spaces and 
two types of individuals. 
The expected behaviour of the nodes in Ciw have been modified such that 
individuals moving from waiting zone 2 into waiting zone 1 get blocked 
if there are more than \(T\) individuals in waiting zone 1.

The same performance measures described in sections 
\ref{sec:waiting_time}, \ref{sec:blocking_time} and 
\ref{sec:proportion_within_target} can also be calculated using the DES model.
The simulation can be ran a number of times to eliminate stochasticity and the
outcomes of the two methods can be directly comparable. 
% TODO Add more documentation (instructions on how to use code)

% TODO: Archive simulation python code

### 2021-08-17 sections/appendix/proportion_within_target_formula/main.tex
Minor change
Make changes suggested by proselint
Apply changes based on Alex's suggestions

In order to consider such measure though one would need to obtain the 
distribution of time in the system for all individuals. 
The complexity of such task lies on the fact that different individuals arrive 
at different states of the Markov model. 
Consider the case when an arrival occurs when the model is at a specific state.

@@

\begin{figure}[ht]
    \centering
    \scalebox{0.75}{
        \input{imgs/example_1242/main.tex}
    }
    \caption{Example Markov model \(C=1, T=2, N=4, M=2\)}
    \label{fig:distribution_of_time_at_specific_state_1_server}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \scalebox{0.75}{\input{imgs/example_2242/main.tex}}
    \caption{Example Markov model \(C=2, T=2, N=4, M=2\)}
    \label{fig:distribution_of_time_at_specific_state_2_servers}
\end{figure}

@@

\paragraph{Specific CDF of hypoexponential distribution}
Equations (\ref{eq:general_cdf_hypoexponential}) and 
(\ref{eq:linear_general_cdf_hypoexponential}) refers to the general CDF of the
hypoexponential distribution where the size of the vector parameters can be of
any size \cite{Favaro2010}.
In the Markov chain models described in figures 
\ref{fig:distribution_of_time_at_specific_state_1_server} and 
\ref{fig:distribution_of_time_at_specific_state_2_servers} the parameter vectors 
of the hypoexponential distribution are of size two, and in fact, for any 
possible version of the investigated Markov chain model the vectors can only be 
of size two.
This is true since for any dimensions of this Markov chain model there will 
always be at most two distinct exponential parameters; the parameter for 
finishing a service (\(\mu\)) and the parameter for moving forward in the queue 
(\(C \mu\)). 
For the special case of \(C=1\) the hypoexponential distribution will not be 
used as this is equivalent to an erlang distribution.
Therefore, by fixing the sizes of \(\vec{r}\) and \(\vec{\lambda}\) to 2, the 
following specific expression for the CDF of the hypoexponential distribution
arises, where the derivative is removed:

@@

This section aims to show that there exists a simplified version of equation 
(\ref{eq:general_cdf_hypoexponential}) that is specific to the proposed Markov 
model.
Function \(\Psi\) is defined using the parameter \(t\) and the variables \(k\) 
and \(l\).
Given the Markov model, the range of values that \(k\) and \(l\) can take can be
bounded.
First of all, from the range of the double summation in equation 
(\ref{eq:general_cdf_hypoexponential}), it can be seen that 
\(k = 1, 2, \dots, \mid \vec{r} \mid\).
Now, \(\mid \vec{r} \mid\) represents the size of the parameter vectors that, 
for the Markov model, will always be 2. 
That is because, for all the exponentially distributed random variables that are
added together to form the new distribution, there only two distinct parameters,
thus forming two erlang distributions. Therefore:

@@

\begin{itemize}
    \item \(k = 2, l = 1\)
    \begin{equation*}
        \begin{split}
            LHS &= - \frac{\partial^{1-1}}{\partial t^{1-1}} 
            \left( \prod_{j=0, j \neq 2}^{2} (\lambda_j + t)^{-r_j} \right) \\
            &=-\left( (\lambda_0 + t)^{-r_0} \times (\lambda_1 + t)^{-r_1} \right) \\
            &=-\left( t^{-1} \times (\lambda_1 + t)^{-r_1} \right) \\ 
            &= - \frac{1}{t(t + \lambda_1)^{r_1}} \\
            & \hspace{7cm} \square
        \end{split}
    \end{equation*}
    \item \(k = 1, l = 1, \dots, r_1\)
    \begin{equation*}
        \begin{split}
            LHS &= -\frac{\partial^{l-1}}{\partial t^{l-1}} 
            \left( \prod_{j=0, j \neq 1}^{2} (\lambda_j + t)^{-r_j} \right) \\
            &= -\frac{\partial^{l-1}}{\partial t^{l-1}}
            \left( (\lambda_o + t)^{-r_0} \times (\lambda_2 + t)^{-r_2} \right) \\
            &= -\frac{\partial^{l-1}}{\partial t^{l-1}}
            \left( \frac{1}{t(t + \lambda_2)}\right)
        \end{split}
    \end{equation*}
    In essence, it only remains to show that:
    \[-\frac{\partial^{l-1}}{\partial t^{l-1}} 
    \left( \frac{1}{t(t + \lambda_2)}\right) = \frac{(-1)^{l} (l-1)!}{\lambda_2}
    \left[\frac{1}{t^l} - \frac{1}{(t + \lambda_2)^l}\right]\]

>>>>

In order to consider such measure though one would need to obtain the 
distribution of time in the system for all individuals. 
The complexity of such task is caused by the fact that different individuals 
arrive at different states of the Markov model. 
Consider the case when an arrival occurs when the model is at a specific state.

@@

\begin{figure}[H]
    \centering
    \scalebox{0.75}{
        \input{imgs/example_1242/main.tex}
    }
    \caption{Example Markov model \(C=1, T=2, N=4, M=2\)}
    \label{fig:distribution_of_time_at_specific_state_1_server}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \scalebox{0.75}{\input{imgs/example_2242/main.tex}}
    \caption{Example Markov model \(C=2, T=2, N=4, M=2\)}
    \label{fig:distribution_of_time_at_specific_state_2_servers}
\end{figure}

@@

\paragraph{Specific CDF of hypoexponential distribution}
Equations (\ref{eq:general_cdf_hypoexponential}) and 
(\ref{eq:linear_general_cdf_hypoexponential}) refers to the general CDF of the
hypoexponential distribution where the size of the vector parameters can be of
any size \cite{Favaro2010}.
In the Markov chain models described in figures 
\ref{fig:distribution_of_time_at_specific_state_1_server} and 
\ref{fig:distribution_of_time_at_specific_state_2_servers} the parameter vectors 
of the hypoexponential distribution are of size two, and in fact, for any 
possible version of the investigated Markov chain model the vectors can only be 
of size two.
This is true since for any dimensions of this Markov chain model there will 
always be at most two distinct exponential parameters; the parameter for 
finishing a service (\(\mu\)) and the parameter for moving forward in the queue 
(\(C \mu\)). 
For the case of \(C=1\) the hypoexponential distribution will not be 
used as this is equivalent to an erlang distribution.
Therefore, by fixing the sizes of \(\vec{r}\) and \(\vec{\lambda}\) to 2, the 
following specific expression for the CDF of the hypoexponential distribution
arises, where the derivative is removed:

@@

This section aims to show that there exists a simplified version of equation 
(\ref{eq:general_cdf_hypoexponential}) that is specific to the proposed Markov 
model.
Function \(\Psi\) is defined using the parameter \(t\) and the variables \(k\) 
and \(l\).
Given the Markov model, the range of values that \(k\) and \(l\) can take can be
bounded.
First, from the range of the double summation in equation 
(\ref{eq:general_cdf_hypoexponential}), it can be seen that 
\(k = 1, 2, \dots, \mid \vec{r} \mid\).
Now, \(\mid \vec{r} \mid\) represents the size of the parameter vectors that, 
for the Markov model, will always be 2. 
That is because, for all the exponentially distributed random variables that are
added together to form the new distribution, there only two distinct parameters,
thus forming two erlang distributions. Therefore:

@@

\begin{itemize}
    \item \(k = 2, l = 1\)
    \begin{equation*}
        \begin{split}
            LHS &= - \frac{\partial^{1-1}}{\partial t^{1-1}} 
            \left( \prod_{j=0, j \neq 2}^{2} (\lambda_j + t)^{-r_j} \right) \\
            &=-\left( (\lambda_0 + t)^{-r_0} \times (\lambda_1 + t)^{-r_1} \right) \\
            &=-\left( t^{-1} \times (\lambda_1 + t)^{-r_1} \right) \\ 
            &= - \frac{1}{t(t + \lambda_1)^{r_1}} \\
            & \hspace{7cm} \square
        \end{split}
    \end{equation*}
    \item \(k = 1, l = 1, \dots, r_1\)
    \begin{equation*}
        \begin{split}
            LHS &= -\frac{\partial^{l-1}}{\partial t^{l-1}} 
            \left( \prod_{j=0, j \neq 1}^{2} (\lambda_j + t)^{-r_j} \right) \\
            &= -\frac{\partial^{l-1}}{\partial t^{l-1}}
            \left( (\lambda_o + t)^{-r_0} \times (\lambda_2 + t)^{-r_2} \right) \\
            &= -\frac{\partial^{l-1}}{\partial t^{l-1}}
            \left( \frac{1}{t(t + \lambda_2)}\right)
        \end{split}
    \end{equation*}
    In essence, it is only needed to show that:
    \[-\frac{\partial^{l-1}}{\partial t^{l-1}} 
    \left( \frac{1}{t(t + \lambda_2)}\right) = \frac{(-1)^{l} (l-1)!}{\lambda_2}
    \left[\frac{1}{t^l} - \frac{1}{(t + \lambda_2)^l}\right]\]

### 2021-08-17 sections/queueing_model/main.tex
Write appendix chapter for DES model
Apply changes based on Alex's suggestions

\section{A queueing model with 2 consecutive buffer centres}

% TODO: If this is to be one paper maybe the first two paragraphs do not need to
% include so much details or even better omit some of the details in the game
% overview section.
In this section, a more in-depth explanation of the queueing model shown in 
figure \ref{fig:diagram_of_queueing_system} will be given.
This is a queuing model that consists of two waiting spaces, one for each type
of individual.

The model consists of two types of individuals; type 1 and type 2.
Type 1 individuals arrive instantly at waiting zone 1 and proceed to wait to
receive their service. 
Type 2 individuals arrive at waiting zone 2 and wait there until they are 
allowed to move to waiting zone 1. 
They are allowed to proceed only when the number of 
individuals in waiting zone 1 \textbf{and} in service is less than a 
pre-determined threshold \(T\).
When the number of individuals is equal to or exceeds this threshold, all second type individuals that arrive will remain 
\textit{``blocked''} in waiting zone 1 until the number of people in the 
system is reduced below \(T\). 
This is shown diagrammatically in figure \ref{fig:diagram_of_queueing_system}.
The parameters of the described queueing model are:

>>>>

\section{A queueing model with 2 consecutive buffer centres}\label{sec:queueing_model}
% TODO: If this is to be one paper maybe the first two paragraphs do not need to
% include so much details or even better omit some of the details in the game
% overview section.
In this section, a more in-depth explanation of the queueing model shown in 
figure \ref{fig:diagram_of_queueing_system} will be given.
This is a queuing model that consists of two waiting spaces, one for each type
of individual.

The model consists of two types of individuals; type 1 and type 2.
Type 1 individuals arrive instantly at waiting zone 1 and proceed to wait to
receive their service. 
Type 2 individuals arrive at waiting zone 2 and wait there until they are 
allowed to move to waiting zone 1. 
They are allowed to proceed only when the number of 
individuals in waiting zone 1 \textbf{and} in service is less than a 
pre-determined threshold \(T\).
When the number of individuals is equal to or exceeds this threshold, all 
second type individuals that arrive will stay 
\textit{``blocked''} in waiting zone 1 until the number of people in the 
system is reduced below \(T\). 
This is shown diagrammatically in figure \ref{fig:diagram_of_queueing_system}.
The parameters of the described queueing model are:
